R Notebook

### 2019-07-15 src/testing_file.Rmd
eeekkk

      rd <- cbind(rd1, rd3, rd4, rd5, rd6, rd7, rd8, rd9, rd10, rd11, rd12)
    #rd <- as.data.frame(rd)
    #rd$month <- as.factor(rd$month)
  }

p <- ggplot(rd2, aes(x=month, y = prob)) + geom_violin(trim=FALSE)
plot(p)

@@

>>>>

@@

}
  rd <- rbind(rd1, rd3, rd4, rd5, rd6, rd7, rd8, rd9, rd10, rd11, rd12)
    #rd <- as.data.frame(rd)
    #rd$month <- as.factor(rd$month)
p <- ggplot(rd, aes(x=month, y = prob)) + geom_violin(trim=FALSE)
plot(p)
